### 2025-07-19 evaluating-prediction-accuracy.qmd
20250719 - citations

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.
In general, projections showed moderate accuracy in predicting players' fantasy performance.
Projections showed moderate accuracy in terms of [discrimination](#sec-discrimination), based on [$R^2$](#sec-coefficientOfDetermination).
However, projections were not highly accurate.
Projections showed some [miscalibration](#sec-calibrationIndices) with respect to actual fantasy points.
In general, projected showed a modest tendency to underpredict performance at lower levels of projected points and a moderate-to-strong tendency overpredict performance at higher levels of projected points, an example of the overextremity form of [miscalibration](#sec-calibration).
As a reminder, the overextremity form of [miscalibration](#sec-calibration) is an example of the overprecision form of [overconfidence](#sec-cognitiveBiasesOverconfidence).
That is, projection sources appear to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their projections of player performance.
Relatedly, crowd-averaged projections tend to be more accurate than individual sources of projections [CITATION].

>>>>

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.
In general, projections showed moderate accuracy in predicting players' fantasy performance.
Projections showed moderate accuracy in terms of [discrimination](#sec-discrimination), based on [$R^2$](#sec-coefficientOfDetermination).
However, projections were not highly accurate.
Projections showed some [miscalibration](#sec-calibrationIndices) with respect to actual fantasy points.
In general, projected showed a modest tendency to underpredict performance at lower levels of projected points and a moderate-to-strong tendency overpredict performance at higher levels of projected points, an example of the overextremity form of [miscalibration](#sec-calibration).
As a reminder, the overextremity form of [miscalibration](#sec-calibration) is an example of the overprecision form of [overconfidence](#sec-cognitiveBiasesOverconfidence).
That is, projection sources appear to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their projections of player performance.
Relatedly, crowd-averaged projections tend to be more accurate than individual sources of projections [@Kartes2024; archived at <https://perma.cc/69F7-LLTN>; @Petersen2017; archived at <https://perma.cc/BG2W-ANUF>].

### 2025-07-19 player-evaluation.qmd
20250719 - citations

Projected statistics (e.g., projected passing touchdowns) are agnostic to league settings and can thus be used to generate league-specific fantasy projections and rankings.
Thus, projected statisitics may be more useful than rankings because they can be used to generate rankings for your particular league settings.
For instance, if you know how many touchdowns, yards, and interceptions a Quarterback is a projected to throw (in addition to any other relevant categories for the player, e.g., rushing yards and touchdowns), you can calculate how many fantasy points the Quarterback is expected to gain in your league (or in any league).
Thus, you can calculate ranking from projections, but you cannot reverse engineer projections from rankings.

@@

Uncertainty is not necessarily a bad characteristic of a player's projected points.
It just means we have less confidence about how the player may be expected to perform.
Thus, players with greater uncertainty are risky and tend to have a higher upside (or ceiling) and a lower downside (or floor).

>>>>

Projected statistics (e.g., projected passing touchdowns) are agnostic to league settings and can thus be used to generate league-specific fantasy projections and rankings.
Thus, projected statistics may be more useful than rankings because they can be used to generate rankings for your particular league settings.
For instance, if you know how many touchdowns, yards, and interceptions a Quarterback is a projected to throw (in addition to any other relevant categories for the player, e.g., rushing yards and touchdowns), you can calculate how many fantasy points the Quarterback is expected to gain in your league (or in any league).
Thus, you can calculate ranking from projections, but you cannot reverse engineer projections from rankings.
Moreover, projections have been shown to be more accurate than rankings [@Petersen2016d; archived at <https://perma.cc/KEZ9-WRB6>].

@@

Uncertainty is not necessarily a bad characteristic of a player's projected points.
It just means we have less confidence about how the player may be expected to perform.
Thus, players with greater uncertainty are risky and tend to have a higher upside (or ceiling) and a lower downside (or floor).
For this reason, identifying players with a high uncertainty can be useful for identifying potential "sleepers"—i.e., late-round draft picks who outperform expectations [@Petersen2014; archived at <https://perma.cc/K6LX-85A4>].
